Improvement of crash forces in structures using optimization tools.

### 2016-07-26 paper.tex
Avances

\documentclass[cmfonts]{witpress}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{cleveref}
\bibliographystyle{witpress}

@@

\begin{table}
	\centering
	\begin{tabular}{llrl}
		\toprule
		Parameter & Description & Value & \\
		\midrule
		$E_{N}$ & Stiffness in normal direction & $\num{5e9}$ & $\si{\kN/\m^2}$ \\
		$E_{T}$ & Stiffness in an in-plane direction & $\num{8e7}$ & $\si{\kN/\m^2}$ \\
		\bottomrule
	\end{tabular}
	\caption[Loctite Hysol 9514 parameters.]{Loctite Hysol 9514 parameters. Taken from \cite{Scattina2011}.}
	\label{tab:ads_params}
\end{table}

@@

		\toprule

@@

		\midrule

@@

		\bottomrule

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/steel}
	\caption{Steel stress-strain curve up to $\num{0.6}\text{\textperthousand}$ strain rate.}
	\label{fig:steel}
\end{figure}

@@

As \cite{Hale} explains, in explicit dynamic modelling, the total running time depends both on the model size (mesh size and total modelled time span) and in the time step size (${\Delta}t$). \Acrfull{SDT} is the maximum time step that still grants the numerical stability of the calculations, by supressing the possibility to a mechanical stress wave to go through more than one element in each time step. This condition is known as the Courant condition:

@@

As COH3D were specifically formulated for adhesive modelling, among other uses, they have been widely used to model this material, in Abaqus \cite{Sadowski2010, Sadowski2011, Sadowski2014, Alvarez2014} and in other software packages \cite{Sato2000, Carlberger2007, Loureiro2010, Scattina2011, Ghasemnejad2013}, although this is not the only existing formulation \cite{Sato2000, Greve2007, Liao2011, Yang2012}. Certain stress distributions cannot be properly modelled, such as in-plane compression, but these have no interest or negligible effects. In Abaqus, these elements are denominated \acrshort{COH3D} and require that:
\begin{itemize}
	\item There can only be a single layer of elements.

>>>>

\documentclass[cmfonts]{witpress}
\usepackage{todonotes}
\usepackage{siunitx}
\usepackage{amsmath}
\usepackage{cleveref}
\bibliographystyle{witpress}

@@

\begin{table}
	\centering
	\begin{tabular}{llrl}
		Parameter & Description & Value & \\

		$E_{N}$ & Stiffness in normal direction & $\num{5e9}$ & $\si{\kN/\m^2}$ \\
		$E_{T}$ & Stiffness in an in-plane direction & $\num{8e7}$ & $\si{\kN/\m^2}$ \\
	\end{tabular}
	\caption[Loctite Hysol 9514 parameters.]{Loctite Hysol 9514 parameters. Taken from \cite{Scattina2011}.}
	\label{tab:ads_params}
\end{table}

@@

@@

@@

@@

\begin{figure}
	\centering
	\includegraphics[width=0.7\linewidth]{figures/IMG_CUTRES/steel}
	\caption{Steel stress-strain curve up to $\num{0.0006}$ strain rate.}
	\label{fig:steel}
\end{figure}

@@

As \cite{Hale} explains, in explicit dynamic modelling, the total running time depends both on the model size (mesh size and total modelled time span) and in the time step size (${\Delta}t$). SDT is the maximum time step that still grants the numerical stability of the calculations, by supressing the possibility to a mechanical stress wave to go through more than one element in each time step. This condition is known as the Courant condition:

@@

As COH3D were specifically formulated for adhesive modelling, among other uses, they have been widely used to model this material, in Abaqus \cite{Sadowski2010, Sadowski2011, Sadowski2014, Alvarez2014} and in other software packages \cite{Sato2000, Carlberger2007, Loureiro2010, Scattina2011, Ghasemnejad2013}, although this is not the only existing formulation \cite{Sato2000, Greve2007, Liao2011, Yang2012}. Certain stress distributions cannot be properly modelled, such as in-plane compression, but these have no interest or negligible effects. In Abaqus, these elements are denominated COH3D and require that:
\begin{itemize}
	\item There can only be a single layer of elements.
